Cluster Difference Imaging Photometric Survey. III. An Open Cluster With a 300\,pc Halo

### 2021-02-17 cluster_paper/ms.tex
update figures

{\bf Emphasize that figure 1 does not clearly tell us whether or not the halo is really distinct from the field, by eye.}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Reported components of NGC\,2516 in position and
    velocity space.}
    The ``core'', identified by \citet{cantatgaudin_gaia_2018} using
    Gaia DR2, is visually coincident
    with where you would think the cluster is if you looked at it through a pair
    of binoculars.
    The ``halo'' was identified by \citet{kounkel_untangling_2019}
    using a less restrictive membership assignment algorithm (discussed
    in the appendices).
    The ``field'' is a set of randomly drawn and non-overlapping stars
    within a
    $(\alpha, \delta, \pi)$ cone centered on the cluster.
		\label{fig:gaia6d}
	}
\end{figure*}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.75\textwidth]{f2a.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf HR diagram of NGC\,2516, using Gaia EDR3 photometry.}
    The core (black) shows a clean sequence consistent with
    stars with a fixed age and metallicity, and varying mass.  The
    halo (blue) is similar, though somewhat noisier.  The faintest M
    dwarfs in the core and halo are brighter than in the field star
    comparison sample (gray), consistent with these stars having not
    yet reached the ZAMS.
    \label{fig:hr}
  }
\end{figure*}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.75\textwidth]{f3a.pdf}
		}

		\subfloat{
			\includegraphics[width=0.75\textwidth]{f3b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf The core and halo of \cn\ in the space of rotation
    period and Gaia color.}
    The {\it top} plot shows periods against a linear scale, while the
    {\it bottom}  shows them against a logarithmic scale.
		\label{fig:rot}
	}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
    \includegraphics[width=0.49\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Field stars show a different rotation period
  distribution than the kinematically selected members.}
		\label{fig:compstar}
	}
\end{figure}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Gaia-based components of NGC\,2516 in position and
    velocity space, cross-matched against the rotators.}
		\label{fig:gaia6d_x_rotn}
	}
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.75\textwidth]{f8b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Gaia-based components of NGC\,2516 in position and
    velocity space, cross-matched against the rotators, but now in
    physical units.}
    Top: relevant projections. Bottom: binned versus 3d position and
    2d velocity difference.
    Bins have width 25\,pc in position, and 2.0\,km\,s$^{-1}$ in
    velocity.
		\label{fig:physical_x_rotn}
	}
\end{figure*}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Reported components of NGC\,2516 in position and
  velocity space.} The core, identified by
  \citet{cantatgaudin_gaia_2018} using Gaia DR2, is coincident with
  the visual overdensity of stars canonically accepted as ``the
  cluster''.  The halo was identified by
  \citet{kounkel_untangling_2019} using a less restrictive membership
  assignment algorithm (see Appendix~\ref{app:clustering}).  The field
  sample is randomly drawn from a $(\alpha, \delta, \pi)$ cube
  centered on the cluster.  It is difficult to visually distinguish
  the field and the halo samples due to the low volume density of the
  halo stars.
  \label{fig:gaia6d}
	}
\end{figure*}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.85\textwidth]{f2a.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf HR diagram of NGC\,2516.}
    No reddening correction has been applied; the photometric data are
    from Gaia EDR3.  The core (black) shows a main sequence and
    turnoff consistent with stars of a fixed age and metallicity.  The
    halo (blue) is similar, though the binary sequence is less
    well-defined.  The faintest M dwarfs in the core and halo are
    brighter than in the field star comparison sample (gray),
    consistent with these stars having not yet reached the ZAMS.
    \label{fig:hr}
  }
\end{figure*}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
    \includegraphics[width=0.75\textwidth]{f3a.pdf}
		% \subfloat{
		% 	\includegraphics[width=0.75\textwidth]{f3a.pdf}
		% }

		% \subfloat{
		% 	\includegraphics[width=0.75\textwidth]{f3b.pdf}
		% }
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf The core and halo of \cn\ in the space of rotation
    period and dereddened Gaia color.}
    % The {\it top} plot shows periods against a linear scale, while the
    % {\it bottom}  shows them against a logarithmic scale.
    The Pleiades \citep[125\,Myr][]{rebull_rotation_2016a}
    and Praesepe \citep[650\,Myr][]{douglas_poking_2017}
    are shown for reference.
    Stars in the core and the halo of NGC\,2516 are
    gyrochronologically coeval with the Pleiades.
		\label{fig:rot}
	}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
    \includegraphics[width=0.49\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Rotation in NGC\,2516 compared to the field.}
  Stars with Gaia $Rp<13$\,mag in the cluster and field samples were
  considered. (Fainter stars in the field sample were not studied as part
  of the broader CDIPS project).
  The field stars show a different rotation period distribution than
  the kinematically selected NGC\,2516 members.
  \label{fig:compstar}
	}
\end{figure}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Gaia-based components of NGC\,2516 in position and
    velocity space, cross-matched against the rotators.}
    The plotted stars are those with $0.5<(Bp-Rp)_0<1.2$ that meet the
    crowding restrictions described in Section~\ref{subsec:tess}: they
    should have been sufficiently bright and non-crowded to enable
    rotation period detection.
		\label{fig:gaia6d_x_rotn}
	}
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.75\textwidth]{f8b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Gaia-based components of NGC\,2516 in position and
    velocity space, cross-matched against the rotators, in physical
    units.}
    {\it Top:} projections in position and 2d-tangential velocity
    space. {\it Bottom:} radially binned versus 3d position and
    2d velocity difference.
    Bins have width 25\,pc in position, and 2.0\,km\,s$^{-1}$ in
    velocity.
		\label{fig:physical_x_rotn}
	}
\end{figure*}
